---
title: 'Compiling a global database of sap flow measurements: the SAPFLUXNET data workflow'
subtitle: 'XIV MEDECOS & XIII AEET meeting
           Ecoinformatics: data science brings new avenues for ecology Symposium'
author: "Víctor Granda"
output:
  beamer_presentation:
    theme: "Madrid"
    colortheme: "beaver"
    fonttheme: "structuresmallcapsserif"
    slide_level: 2
    includes:
      in_header: mystyle.tex
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## R Markdown
### subtitle here

This is an R Markdown presentation. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.

## Slide with Bullets

- Bullet 1
- Bullet 2
- Bullet 3

## Slide with R Output
left: 70%

```{r cars, echo = TRUE}
summary(cars)
```

***

```{r pressure}
plot(pressure)
```

